Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2022-06-06 Writing/manuscript_gwr.rmd
updated results with five price ratio scenarios: 5%, 25%, 50%, 75%, 95%

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
```

@@

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA. The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.

>>>>

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
library(ggh4x)
```

@@

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff] %>% 
  #=== label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"]
  # .[, pLabel := "Middle"] %>% 
  # .[pRatio==min(pRatio), pLabel := "Low"] %>% 
  # .[pRatio==max(pRatio), pLabel := "High"] %>% 
  # .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA.

, for the two GWR models and three N/corn price ratios. The

Three price ratios (nitrogen fertilizer price divided by corn price, both in $/kg) were used in the simulations: 4.16 (low), 6.56 (medium), and 10.35 (high). They were obtained by taking the 5%, 50%, and 95% of historical monthly price ratios from 1990 to 2022. The recent period (April 2022) corn price of about $0.28/kg was used in the simulation results. Our main scenario to discuss was the medium price ratio, where the nitrogen fertilizer price was $1.8/kg (that was close to the recent market price). Note that this setting may generate some extreme prices. For example, the high price ratio scenario was corresponding to nitrogen price of $2.85/kg, which was unrealistic in history. But that did not affect the EONR estimations since they were only affected by the relative nitrogen-corn price ratio rather than absolute the prices. The final profit values 〖∆Π〗_^* could be over- or under-estimated by extreme prices, but those over- or under-estimations were linear scale-up or scale-down of the actual profit values and would not affect the economic performance rankings of trial designs.

The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.
